grad_weight

### 2022-04-12 inst/grad_weight.Rmd
differentiate WRT D

wanted <- list("p1",NULL,NULL,"p1","p2",NULL,"p2","p3","p3")
wanted

@@

>>>>

wanted <- list("p1",NULL,NULL,"p1","p2",NULL,"p2","p3","p3")

@@

If we wish to differentiate with respect to `D` we need to change the `wanted` list:

```{r}
o <- c("p1","p2")
n <- NULL
wantedD <- list(n,o,n,o,n,n,o,n,n)

diff <- 0
dD <- 1e-5
B <- brackfunc(w,D)
for(i in seq_along(wanted)){
   diff <- diff +  grad_weight_single(H, probs, wpv=B[[i]],wanted=wantedD[[i]])
}

LHS <- diff  # using grad_weight_single()
RHS <- (loglik(probs,f2(w,D=D+dD)) - loglik(probs,f2(w,D)))/dD  # differential via numerics
c(LHS,RHS,LHS-RHS)
```
